\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref} % 必须添加在导言区
\begin{document}
% 修改后的右上角区块
\begin{flushright}
    Zhang Jinrui \\
    \today \\  % 日期
    \href{mailto:jerryzhang40@gmail.com}{\texttt{jerryzhang40@gmail.com}}\\
    \href{mailto:zhangjr1022@mails.jlu.edu.cn}{\texttt{zhangjr1022@mails.jlu.edu.cn}}\\
    Dalian, Liaoning 116021 \\
    +86 13478940406 \\
    \href{https://github.com/yourgithub}{GitHub: yourgithub}
\end{flushright}

\vspace{0.2cm}  % 调整与下方内容的间距

% \begin{flushleft}
%     Polymath Program Committee\\
%     Institute for Advanced Study\\
%     1 Einstein Drive\\
%     Princeton, NJ 08540
% \end{flushleft}
\vspace{0.5cm}

% \begin{flushleft}
%     Polymath Program Committee\\
%     Program Address/Email  % Replace with actual information
% \end{flushleft}

\vspace{1cm}

Dear Polymath Program Selection Committee,

\par\textbf{Opening Statement}
As a third-year mathematics major at Jilin University, I am writing to express my enthusiastic interest in the Polymath Summer Research Program. My research experience in programming and optimal control and demonstrated capacity for collaborative problem-solving align closely with the program's mission to advance mathematical discovery through open collaboration.

% \par\textbf{Research Motivation}
% My recent investigation of [specific problem/project] revealed unexpected connections between [Field A] and [Field B], particularly in the context of [specific phenomenon]. This discovery has motivated me to explore [relevant open problem], where I believe Polymath's distributed approach could yield significant insights. For instance, [briefly describe a concrete problem you've contemplated].

\par\textbf{Technical Preparation}
Through Optimal Control, I have developed:
\begin{itemize}
    \item Advanced proficiency in nonlinear optimization, machine learning.
    \item Expertise with CMake and c/c++, python.
    \item Experience in Category Theroy, Functional programming, abstract algebra and group-convolutional nerual network.
\end{itemize}
My recent work on Differential Informed Auto-Encoder, resulting in a new way to find the inner structure inside dataset, is currently available on arXiv:2410.18593.

\par\textbf{Program-Specific Alignment}
The Polymath initiative particularly resonates
with me because of its
Optimal Control, Nonlinear Optimization and
Geometric Deep Learning. I am eager to contribute
my expertise in programming and mathematical modeling
while learning from the community's program.
This experience would directly support
my long-term goal to make progress in These areas.

\par\textbf{Closing Statement}
I would welcome the opportunity
to discuss how my background in
Machine Learning and
experiences in mathematical modeling
could contribute to
Polymath's ongoing work on .
Thank you for considering my application.

\vspace{0.5cm}

Sincerely,\\
Zhang Jinrui\\
% [Your Address]\\
% [City, State, ZIP Code]\\
% [Email Address]\\
% [Phone Number]\\
% [Personal Website/GitHub (if applicable)]

\end{document}