\documentclass[a4paper,11pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{setspace}

\title{\textbf{Research Statement}}
\author{Zhang Jinrui}
\date{March 2025}

\begin{document}

\maketitle
\onehalfspacing

\section*{Introduction}
Using mathematics to tackle with real world
problem is always what I want to do.
My primary research interests lie
in \textbf{Optimal
    Control, Machine Learning,
    and Dynamical Systems}.
In particular,
I am interested in
leveraging optimization
techniques and
computational methods to
address complex
mathematical and real-world problems.
Through the Polymath Summer Research
Program, I hope to engage in
to have more practice in problem-solving
and team collaboration.

\section*{Previous Research Experience}
During my undergraduate studies at Jilin University, I actively participated in research projects involving \textbf{optimization, differential equations, and machine learning}. One of my most significant projects was \textit{Differential Informed Auto-Encoder}\cite{zhang2024differentialinformedautoencoder}, where I explored methods to extract underlying differential structures from datasets. By applying techniques from \textbf{numerical analysis and differential equations}, I developed an algorithm that automatically identifies governing differential equations from data.

Additionally, I have employed computational methods to analyze mathematical problems, developing algorithms in \textbf{C/C++ and Python} to numerically approximate and validate theoretical results.

\section*{Current Research Interests}
My current research focuses on the intersection of \textbf{optimization, differential equations, and dynamical systems}. Specifically, I aim to use the
methods and concept of optimazaiton to
tackle with the Differential equations and dynamical systems problems.

Through the Polymath program, I hope to contribute to collaborative mathematical research while refining my ability to tackle real-world problems. I am particularly excited about engaging with researchers who share my passion for solving real world practical problems.

\section*{Future Goals}
Looking ahead, I aim to further integrate \textbf{mathematical optimization with real-world applications}, particularly in areas such as \textbf{optimal control and differential equation-based modeling}. My goal is to develop computationally efficient methods that bridge the gap between theoretical mathematics and practical problem-solving.

\section*{Conclusion}
The Polymath Summer Research Program presents a unique opportunity to collaborate with leading researchers and peers in tackling significant mathematical challenges. With my strong analytical background, research experience, and enthusiasm for mathematical exploration, I am confident that I can contribute meaningfully to the program while gaining invaluable academic experience.

\bibliographystyle{plain}  % or another style like unsrt, IEEEtran, etc.
\bibliography{references}  % Ensure you have a valid references.bib file

\end{document}
